---
title: "bootstrapping"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```


## Simulate data

```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const |> 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```

Plot the datasets

```{r}
sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df |> 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source) 
```


fitting linear regressions to both:'

```{r}
lm(y ~ x, data = sim_df_const) |> 
  broom::tidy() |> 
  knitr::kable(digits = 3)
```

now non constant

```{r}
lm(y ~ x, data = sim_df_nonconst) |> 
  broom::tidy() |> 
  knitr::kable(digits = 3)
```


Now let's use the bootstrap to make an inference on the data

## Draw one bootstrap sample

```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```
we made a function so we can reuse it
let's check if it works

```{r}
boot_sample(sim_df_nonconst)
```


```{r}
boot_sample(sim_df_nonconst) |> 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")
```


## Many samples and analysis

```{r}
boot_straps = 
  tibble(strap_number = 1:1000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(df = sim_df_nonconst))
  )

boot_straps

```

lets look at the first few elements

```{r}
boot_straps |> 
  slice(1:3) |> 
  mutate(strap_sample = map(strap_sample, \(s) arrange(s, x))) |> 
  pull(strap_sample)
```

can I run an analysis on each of these?

```{r}
bootstrap_results = 
  boot_straps |> 
  mutate(
    models = map(strap_sample, \(df) lm(y ~ x, data = df) ),
    results = map(models, broom::tidy)) |> 
  select(-strap_sample, -models) |> 
  unnest(results) 
```

what do I have now?

```{r}
bootstrap_results |> 
  group_by(term) |> 
  summarize(boot_se = sd(estimate)) |> 
  knitr::kable(digits = 3)

```

Lets use the bootstrap estimates to construct the confidence interval

Construct bootstrap CI

```{r}
bootstrap_results |> 
  group_by(term) |> 
  summarize(
    ci_lower = quantile(estimate, 0.025), 
    ci_upper = quantile(estimate, 0.975))
```


```{r}
boot_straps |> 
  unnest(strap_sample) |> 
  ggplot(aes(x = x, y = y)) + 
  geom_line(aes(group = strap_number), stat = "smooth", method = "lm", se = FALSE, alpha = .1, color = "blue") +
  geom_point(data = sim_df_nonconst, alpha = .5)
```



## Bootstrap using modelr

```{r}
boot_straps = 
  sim_df_nonconst |> 
  modelr::bootstrap(n = 1000)

boot_straps |> pull(strap) |> nth(1)
```

```{r}
boot_straps |> pull(strap) |> nth(1) |> as_tibble()
```

repeat bootstrap analysis:

```{r}
sim_df_nonconst |> 
  modelr::bootstrap(n = 1000) |> 
  mutate(
    models = map(strap, \(df) lm(y ~ x, data = df) ),
    results = map(models, broom::tidy)) |> 
  select(-strap, -models) |> 
  unnest(results) |> 
  group_by(term) |> 
  summarize(boot_se = sd(estimate))
```





