---
title: "cross_validation"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
```


```{r}
library(p8105.datasets)

set.seed(1)
```


## Simulate data

```{r}
data("lidar")

lidar_df = 
  lidar |> 
  as_tibble() |>
  mutate(id = row_number())
```

Look at the data in graph and understand that is in not a linear graph

```{r}
lidar_df |> 
  ggplot(aes(x = range, y = logratio)) + 
  geom_point()
```

## Cross validation -- by hand

Get training and testing datasets

```{r}
train_df = sample_frac(lidar_df, size = .8)
test_df = anti_join(lidar_df, train_df, by = "id")
```


Graph below
```{r}
ggplot(train_df, aes(x = range, y = logratio)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```


Fit three models
```{r}
linear_mod = lm(logratio ~ range, data = train_df)
smooth_mod = mgcv::gam(logratio ~ s(range), data = train_df)
wiggly_mod = mgcv::gam(logratio ~ s(range, k = 30), sp = 10e-6, data = train_df)
```

Lets see the models: aka can I see what I just did?

```{r}
train_df |> 
  add_predictions(smooth_mod) |> 
  ggplot(aes(x = range, y = logratio)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

```{r}
train_df |> 
  add_predictions(wiggly_mod) |> 
  ggplot(aes(x = range, y = logratio)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")
```



Let's see all three models together

```{r}
train_df |> 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = range, y = logratio)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") + 
  facet_wrap(~model)
```

Look at precision accuracy

```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

the smooth is the best one!

## Cross validation using `modelr`

```{r}
cv_df = 
  crossv_mc(lidar_df, 100) 
```

what is happening here...

```{r}
cv_df |> pull(train) |> nth(1) |> as_tibble()
cv_df |> pull(test) |> nth(1) |> as_tibble()
```

```{r}
cv_df =
  cv_df |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

Let's try to fit models and get RMSEs for them.

```{r}
cv_df = 
  cv_df |> 
  mutate(
    linear_mod  = map(train, \(df) lm(logratio ~ range, data = df)),
    smooth_mod  = map(train, \(df) gam(logratio ~ s(range), data = df)),
    wiggly_mod  = map(train, \(df) gam(logratio ~ s(range, k = 30), sp = 10e-6, data = df))) |> 
  mutate(
    rmse_linear = map2_dbl(linear_mod, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_smooth = map2_dbl(smooth_mod, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_wiggly = map2_dbl(wiggly_mod, test, \(mod, df) rmse(model = mod, data = df)))
```

Plot this into a graph:

```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```





