---
title: "review_all"
output: github_document
date: October 7th 2025
---

## What is Data Science?

I'm reviewing from the first week of classes to the 6th week of classes. First,
DEF: data science is the study of formulating and rigorously answering
questions using a data-centric process that emphasizes clarity, reproducibility,
effective communication, and ethical practices.


From this lecture we learn how to load a package.

```{r}
library(tidyverse)
```

Okay now we load a tidy example data set

```{r}
library(p8105.datasets)
data("weather_df")
```

Using `help("weather_df")` we can have R tell us what is in the data.

Now here is an advanced visualization of this data using `ggplot` 

```{r}
weather_df |> 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) +
  theme(legend.position = "bottom")
```





## Best Practices

welcome to lecture 2, this should be okay.

```{r}
library(tidyverse)
```

To save variables in R you must assign it to something

```{r}
x = 2 + 3
y = c(1, 3, 5, 7)
```

now you can recall the variables for different things. Also `c()` means a 
collection of numbers! So this code assigns variables.

```{r}
x+y
```

So now we will overwrite x, using a random number generation for x amount of #'s

```{r}
x = runif(n = 20)
view(x)
```

to find info abt a code you might not know u can ask R
```{r}
?runif
```


DATAAA
FRAMEEEEESSSS
-------------------------------------Let's make one!

```{r}
example_df = tibble(
  vec_numeric = 1:4,
  vec_char = c("my","name","is","yasmine"),
  vec_factor = factor(c("male", "male","female","female"))
)
```

so the `tibble` function helps us create the data frame table. using the vec...
we can fill in/ create out table.

if you don't label the df, then you will have to code everything each time.

Let's plot

```{r}
plot_df = tibble(
  x = rnorm(100, sd = .5),
  y = 1 +2 * x + rnorm(100)
)

ggplot(plot_df, aes(x = x)) + geom_histogram()

ggplot(plot_df, aes(x = x, y = y)) + geom_point()

```




