---
title: "review_all"
output: github_document
date: October 7th 2025
---

# What is Data Science?

I'm reviewing from the first week of classes to the 6th week of classes. First,
DEF: data science is the study of formulating and rigorously answering
questions using a data-centric process that emphasizes clarity, reproducibility,
effective communication, and ethical practices.


From this lecture we learn how to load a package.

```{r}
library(tidyverse)
```

Okay now we load a tidy example data set

```{r}
library(p8105.datasets)
data("weather_df")
```

Using `help("weather_df")` we can have R tell us what is in the data.

Now here is an advanced visualization of this data using `ggplot` 

```{r}
weather_df |> 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) +
  theme(legend.position = "bottom")
```





# Best Practices

welcome to lecture 2, this should be okay.

```{r}
library(tidyverse)
```

To save variables in R you must assign it to something

```{r}
x = 2 + 3
y = c(1, 3, 5, 7)
```

now you can recall the variables for different things. Also `c()` means a 
collection of numbers! So this code assigns variables.

```{r}
x+y
```

So now we will overwrite x, using a random number generation for x amount of #'s

```{r}
x = runif(n = 20)
view(x)
```

to find info abt a code you might not know u can ask R
```{r}
?runif
```


### Make a data frame

```{r}
example_df = tibble(
  vec_numeric = 1:4,
  vec_char = c("my","name","is","yasmine"),
  vec_factor = factor(c("male", "male","female","female"))
)
```

so the `tibble` function helps us create the data frame table. using the vec...
we can fill in/ create out table.

if you don't label the df, then you will have to code everything each time.

Let's plot

```{r}
plot_df = tibble(
  x = rnorm(100, sd = .5),
  y = 1 +2 * x + rnorm(100)
)

ggplot(plot_df, aes(x = x)) + geom_histogram()

ggplot(plot_df, aes(x = x, y = y)) + geom_point()

```


Oh btw to save the plot we would do:
```{r}
ggsave("scatter_plot_review.pdf", height = 4, width = 4)
```


# Writing with Data!
Restart R using session tab on top

I kind already know how to use r markdown documents bc im doing that rn lol.

First know that using **, around your words make bold and _ before and after_ 
makes: _this_ vs the first one which is **this**


### Making a data frame from plot

the code chunk below creates a data frame and generates a plot.

```{r}
library(tidyverse)

plot2_df = tibble(
  x = rnorm(500, mean = 2, sd = 4),
  y = 3 - 4.2 * x + rnorm(500)
)

ggplot(plot2_df, aes(x = x, y = y)) + geom_point()
```


Know that in editing the `{r}` section, you can make
things disappear from the final doc that is in our viewer. 

using `echo = FALSE` you can hide the code you used to make the plot
using `message = FALSE` you turn off the messages so the study after you load a
package.

I will also code the data frame has `r nrow(plot_df)`rows. 
      so using inline code ` ` and putting in nrow(your_df_here), the R will
      code automatically for you the number of rows. 

#### Here is a list

using * we can make lists:

* This is my first list item
* we need at least two items
  * using tab here is a sub item
* third list thang

#### Lets make a Table

Col 1 | Col 2
----- | -----
a     | b   

> Now to make a block quote use this `>` and then type


Let's see if I can do a quick learning assessment:

```{r la}
la_df = tibble(
  norm_samp = rnorm(500, mean = 1),
  norm_samp_pos = norm_samp > 0,
  abs_norm_samp = abs(norm_samp)
)

ggplot(la_df, aes(x = abs_norm_samp)) + geom_histogram()

median_samp = median(pull(la_df, norm_samp))


```


Here you can find the median rounded `r round (median_samp, digits = 2)`.

Lets write a list of our previous sample
*`r mean(pull(la_df, norm_samp))`
*`r median(pull(la_df, norm_samp))`
* `r sd(pull(la_df, norm_samp))`


# Git and Github

Yay let's start class 4. Luckily, I actually remember how to do most of this
as we are currently using git for this document. lol!

no need to review this information, we can now move onto the **HARD** stuff.

say a _prayer_. 
















