---
title: "review_viz1"
output: github_document
---

```{r message=FALSE}
library(tidyverse)
library(ggridges)

```


## Load weather data

```{r}
library(p8105.datasets)
data("weather_df")

weather_df
```

##scatterplots

create one!
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

new approach same plot
```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

save and edit plot
```{r}
weather_plot =
  weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) 

weather_plot + geom_point()
```

## advanced scatterplot
start with the same one and make it fancy

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth(se = FALSE)
```

what abt aes placement

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()
```

Let's facet some things!

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.5) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

Let's combine some elements and try a new plot

```{r}
weather_df |> 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```


## some small notes
how many geoms have to exist?

you can have whatever geoms you want.

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```

You cab use a beat geom

```{r}
weather_df |> 
  ggplot(aes( x = tmin, y = tmax)) +
  geom_density_2d() +
  geom_point(alpha = .3)

```


## univariate plots

Histogram are great

```{r}
weather_df |> 
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

can we add color?
```{r}
weather_df |> 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram(position = "dodge")
```

u can also do this but like then u have to hope ur range is the same etc

```{r}
weather_df |> 
  ggplot(aes(x = tmin)) +
  geom_histogram() +
  facet_grid(. ~ name)
```

 so how would i do a univariate plot histogram?
 
 lets try a new geometry
 
```{r}
weather_df |> 
  ggplot(aes (x = tmin, fill = name)) +
  geom_density(alpha = .3)
```
 like a smoother histogram.. if u add after alpha .3, adjust = .5 is can be more
 detailed
 
 boxplots
```{r}
weather_df |> 
  ggplot(aes(x = name, y = tmin)) +
  geom_boxplot()
```
 
Trendy plots!

```{r}
weather_df |> 
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin(alpha = .5) +
  stat_summary()
```

stat_summary = mean... and standard error in the data

Ridge plots
```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = name)) +
  geom_density_ridges()
```

vs the regular geom_density.

# save and embed


Let's save a scaterplot

```{r}
weather_plot2 = 
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5)

ggsave("review_all_files/weather_plot2.pdf", weather_plot2, width = 8, height = 5)
```
 how to saveee thinfs.
 
 u can also just do `ggsave("weather_plot2.pdf", weather_plot2)

embed at different sze

```{r, fig.width=12, fig.height=6}
weather_plot2
```







