---
title: "review_all_two"
output: github_document
---

# Data wrangling 1

Let's go!

```{r setup}
library(tidyverse)
library(readxl)
library(haven)
```

lets read in some data and clean names

```{r}
litters_df = read_csv("data/FAS_litters.csv")
litters_df =
  janitor::clean_names(litters_df)
```

lets look at info

Printing in the console
```{r}
tail(litters_df)

# looking at the last row of data

skimr::skim(litters_df)

#when you have characters variables is give u a histogram, sd, mean, max, min, info missing

```

so we have <chr> variables that have letters and numbers, then we have <dbl> 
which are numeric variables.


#### options to read_csv

```{r}
litters_df = read_csv("data/FAS_litters.csv", skip = 10, col_names = FALSE,
                      na = c("", "NA", ".", "999"))

# here we are skipping the first 10 lines of data, and then we don't want the
# data to be whatever so we make R make random column names for the table. and
# na tells the data that those things are missing numbers like 

```

when you put ?read_csv... you can learn about this function. more info.

Now lets read in different files
#### read in an excel file

```{r}
mlb_df = read_excel("data/mlb11.xlsx", range = "A1:F7")
mlb_df
# this data set was already cleaned
```

remember you can use ?read_excel to get more info. 

Now lets read in a SAS file

```{r}
pulse_df = read_sas("data/public_pulse_data.sas7bdat")
pulse_df = janitor::clean_names(pulse_df)

```













