---
title: "review_hw1"
output: github_document
---
```{r problem 1, message = FALSE}
library(tidyverse)

```

The hw asks us to `install.packages("moderndive")` but in the console!
Do that here.

Let's now load the code

```{r code}
library(moderndive)
data("early_january_weather")
```

Okay, this data set `early_january_weather` is telling us about the hourly
meteorological data for LGA, JFK, and EWR in the month of January 2013.

Variables are origin, date, hour, temp (F), dewp(F), humid, wind_dir(degrees),
wind_speed (mph), wind_gust(mph), precip (in), pressure, visib, time_hour.

The data set has `r nrow(early_january_weather)` rows and 
`r ncol(early_january_weather)` variables or columns.

### Let's make a scatterplot

```{r scatterplot}
early_df = ggplot(data = early_january_weather,
                  aes( x = time_hour, 
                       y = temp, 
                       color = humid)
                  )+ geom_point()

ggsave("review_all_early_df.pdf")

```


don't forget to add `geom_point` at the end to have points on the plot.

to make a `ggsave`, create a title for your image and then add .pdf 






