---
title: "simulation"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6 ,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "virids"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## let's simulate something
I have a function

```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data |> 
    summarize(
      mean = mean(x),
      sd = sd(x)
    )
}
```

I can "simulate" by running this line.
```{r}
sim_mean_sd(30)
```

## Let's simulate alot

Let's start with a for loop

```{r}
output = vector("list", 100)

for (i in 1:100) {
  
  output[[i]] = sim_mean_sd(30)
}

bind_rows(output)
```

Let's use a loop function.

```{r}
sim_results =
  rerun(100, sim_mean_sd(30)) |> 
  bind_rows()
```

Let's look at results...

```{r}
sim_results |> 
  ggplot(aes(x = mean)) + geom_density()

sim_results |> 
  summarize(
    avg_samp_mean = mean(mean),
    sd_samp_mean = sd(mean)
  )
```


## Let's try other sample sizes.


```{r}
sim_results |> 
  pivot_longer(
    mean:sd,
    names_to = "parameter", 
    values_to = "estimate") |> 
  group_by(parameter) |> 
  summarize(
    emp_mean = mean(estimate),
    emp_sd = sd(estimate)) |> 
  knitr::kable(digits = 3)

```


short hand run:
```{r}
sim_results_df =   
  map(1:100, \(i) sim_mean_sd(30, 2, 3)) |> 
  bind_rows()

```


simulation: mean for several n's 

```{r}
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    iter = 1:1000
  ) |> 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) |> 
  unnest(estimate_df)
```

look at mean estimates across sample sizes

```{r}
sim_results_df |> 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) |> 
  ggplot(aes(x = sample_size, y = mean, fill = sample_size)) + 
  geom_violin()

```

as the sample size grows, the width of the distribution shrinks.

Look at empirical mean and variance.

```{r}
sim_results_df |> 
  pivot_longer(
    mean:sd,
    names_to = "parameter", 
    values_to = "estimate") |> 
  group_by(parameter, sample_size) |> 
  summarize(
    emp_mean = mean(estimate),
    emp_var = var(estimate)) |> 
  knitr::kable(digits = 3)
```


## Simulation for one n

creating a function:
```{r}
sim_regression = function(n, beta0 = 2, beta1 = 3) {
  
  sim_data = 
    tibble(
      x = rnorm(n, mean = 1, sd = 1),
      y = beta0 + beta1 * x + rnorm(n, 0, 1)
    )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}
```

run it 500 times:

```{r}
sim_results = 
  expand_grid(
    sample_size = 30,
    iter = 1:500
  ) |> 
  mutate(
    estimate_df = map(sample_size, sim_regression)
  ) |> 
  unnest(estimate_df)
```


now we plot this:

```{r}
sim_results |> 
  ggplot(aes(x = beta0_hat, y = beta1_hat)) + 
  geom_point()
```


in the p8105.com we do one more example where we learn that: For both true SDs, increasing the sample size results in a narrower distribution, and the distribution of the sample mean is wider when the true SD is larger.


















