---
title: "strings_and_factors"
output: github_document
---
```{r}
library(tidyverse)
library(rvest)
library(p8105.datasets)
```


## Strings and  regex

```{r}
string_vec = c("my", "name", "is", "yasmine")

str_detect(string_vec, "e")
str_replace(string_vec, "yasmine", "Yasmine")
```

uppercase is sensitive in strings

```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun",
  "it will be fun, i think"
)

str_detect(string_vec, "i think")
str_detect(string_vec, "^i think")
str_detect(string_vec, "i think$")
```

^ means the beginning
$ ending in i think

```{r}
string_vec = c(
  "Time for a Pumpkin Spice Latte!",
  "went to the #pumpkinpatch last weekend",
  "Pumpkin Pie is obviously the best pie",
  "SMASHING PUMPKINS -- LIVE IN CONCERT!!"
  )

str_detect(string_vec, "[Pp]umpkin")
```

that above was to select both capital and lowercase P

```{r}
string_vec = c(
  '7th inning stretch',
  '1st half soon to begin. Texas won the toss.',
  'she is 5 feet 4 inches tall',
  '3AM - cant sleep :('
  )

str_detect(string_vec, "^[0-9][a-zA-Z]")

```

what about a number followed by letters? then you would do what is above. 


```{r}
string_vec = c(
  'Its 7:11 in the evening',
  'want to go to 7-11?',
  'my flight is AA711',
  'NetBios: scanning ip 203.167.114.66'
  )

str_detect(string_vec, "7.11")
str_detect(string_vec, "7\\.11") 

```

"." caputres everything, so all the 7(something)11
the second one, you must use \\ to say that the . is looking for an actual 
dot and not just any character

```{r}
string_vec = c(
  'The CI is [2, 5]',
  ':-]',
  ':-[',
  'I found the answer on pages [6-7]'
  )

str_detect(string_vec, "\\[")
```

this is to enforce what we just learned to find an actual open bracket

## Factors

```{r}

```







