---
title: "strings_and_factors"
output: github_document
---
```{r}
library(tidyverse)
library(rvest)
library(p8105.datasets)
```


## Strings and  regex

```{r}
string_vec = c("my", "name", "is", "yasmine")

str_detect(string_vec, "e")
str_replace(string_vec, "yasmine", "Yasmine")
```

uppercase is sensitive in strings

```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun",
  "it will be fun, i think"
)

str_detect(string_vec, "i think")
str_detect(string_vec, "^i think")
str_detect(string_vec, "i think$")
```

^ means the beginning
$ ending in i think

```{r}
string_vec = c(
  "Time for a Pumpkin Spice Latte!",
  "went to the #pumpkinpatch last weekend",
  "Pumpkin Pie is obviously the best pie",
  "SMASHING PUMPKINS -- LIVE IN CONCERT!!"
  )

str_detect(string_vec, "[Pp]umpkin")
```

that above was to select both capital and lowercase P

```{r}
string_vec = c(
  '7th inning stretch',
  '1st half soon to begin. Texas won the toss.',
  'she is 5 feet 4 inches tall',
  '3AM - cant sleep :('
  )

str_detect(string_vec, "^[0-9][a-zA-Z]")

```

what about a number followed by letters? then you would do what is above. 


```{r}
string_vec = c(
  'Its 7:11 in the evening',
  'want to go to 7-11?',
  'my flight is AA711',
  'NetBios: scanning ip 203.167.114.66'
  )

str_detect(string_vec, "7.11")
str_detect(string_vec, "7\\.11") 

```

"." caputres everything, so all the 7(something)11
the second one, you must use \\ to say that the . is looking for an actual 
dot and not just any character

```{r}
string_vec = c(
  'The CI is [2, 5]',
  ':-]',
  ':-[',
  'I found the answer on pages [6-7]'
  )

str_detect(string_vec, "\\[")
```

this is to enforce what we just learned to find an actual open bracket

## Factors

```{r}
factor_vec = factor(c("male", "male","female","female"))

factor_vec

as.numeric(factor_vec)

```

what happens if i re level....

```{r}
factor_vec = fct_relevel(factor_vec, "male")

factor_vec

as.numeric(factor_vec)

```


##NSDUH


```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

table_marj = 
  read_html(nsduh_url) |> 
  html_table() |> 
  first() |>
  slice(-1)

```

we are going to edit the data to make them clearer.

```{r}
data_marj =
  table_marj |> 
  select(-contains("P Value")) |> 
  pivot_longer(
    -State,
    names_to = "age_year",
    values_to = "percent"
  ) |> 
  separate(age_year, into = c("age","year"), sep = "\\(") |> 
  mutate(
    year = str_replace(year, "\\)", ""),
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent)
  ) |> 
   filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
  
```


Let's continue with the data set. we just tidyed the data!





















