---
title: "writing_functions"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

set.seed(1)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continous.colour = "viridis",
  ggplot2.continous.fill = "viridis"
)

scale_color_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Do something simple

```{r}
x_vec = rnorm(25, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```

I want a function to compute z-scores

```{r}
z_scores = function(x){
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least 3 numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
}

z_scores(x_vec)
```

Try my function on some other things

* you cant do z_scores on the number 3 or a phrase "my name is yasmine"

```{r, error=TRUE}
z_scores(3)
z_scores("my name is yasmine")
z_scores(mtcars)
z_scores(c(TRUE, TRUE, FALSE, TRUE))
```


## Multiple outputs

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

check that the function works

```{r}
x_vec = rnorm(1000, mean = 3, sd = 4)
mean_and_sd(x_vec)
```


## Multiple inputs

```{r}
sim_data = tibble(
  x = rnorm(30, mean = 2, sd = 3)
)

sim_data |> 
  summarize(
    mu_hat = mean(x),
    sigma_hat = sd(x)
  )

```
Lets do this with a function


```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = 
    tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data |> 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}

sim_mean_sd(100,6,3)
```


```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = 
    tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data |> 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}

sim_mean_sd( n = 100, mu = 6,sigma = 3)
```


```{r}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") |>
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") |>
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") |>
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) |>
  janitor::clean_names() |>
  pivot_longer(
    female:male,
    names_to = "sex",
    values_to = "words") |> 
  mutate(race = str_to_lower(race)) |> 
  select(movie, everything()) 
```


so that was repetative. here is a function that makes life easy

```{r}
lotr_load_and_tidy = function(path, range, movie_name) {
  
  df = 
    readxl::read_excel(path, range = range) |>
    janitor::clean_names() |>
    pivot_longer(
      female:male,
      names_to = "sex",
      values_to = "words") |>
    mutate(
      race = str_to_lower(race),
      movie = movie_name) |> 
    select(movie, everything())
  
  df
  
}

lotr_tidy = 
  bind_rows(
    lotr_load_and_tidy("data/LotR_Words.xlsx", "B3:D6", "fellowship_ring"),
    lotr_load_and_tidy("data/LotR_Words.xlsx", "F3:H6", "two_towers"),
    lotr_load_and_tidy("data/LotR_Words.xlsx", "J3:L6", "return_king"))
```

function as an argumet

```{r}
x_vec = rnorm(25, 0, 1)

my_summary = function(x, summ_func) {
  summ_func(x)
}

my_summary(x_vec, sd)

my_summary(x_vec, IQR)
my_summary(x_vec, var)
```




## Scoping
this can be confusing and problematitc bc y exisits in the environemtn and not as 
an argument
```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)
```


